tSZ $\times$ galaxies

### 2019-04-01 notes/notes.tex
updated notes, added 1h-2h split when plotting

The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
\begin{equation}
  P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
\end{equation}
Each of these can be estimated in terms of the Fourier-space profiles as:
\begin{align}
  &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,U(k|M)\,V(k|M)\\
  &P^{2h}_{UV}(k)=P_L(k)\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,U(k|M)\right]\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,V(k|M)\right].
\end{align}
Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function and $b_h(M)$ is the halo bias.

@@

\end{itemize}
We will start by implementing these as defined in the papers, and then decide which parameters of them to free up (an obvious one is $1-b$, but we may want to be more general than that).

@@

>>>>

The halo model prediction for the cross-power spectrum $P_{UV}$ then consists of two contributions, from the so-called 1-halo term and 2-halo term:
\begin{equation}
  P_{UV}(k)=P^{1h}_{UV}(k)+P^{2h}_{UV}(k).
\end{equation}
Each of these can be estimated in terms of the Fourier-space profiles as:
\begin{align}
  &P^{1h}_{UV}(k)=\int dM\,\frac{dn}{dM}\,\langle U(k|M)\,V(k|M)\rangle\\
  &P^{2h}_{UV}(k)=P_L(k)\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,\langle U(k|M)\rangle\right]\,\left[\int dM\frac{dn}{dM}\,b_h(M)\,\langle V(k|M)\rangle\right].
\end{align}
Here, $P_L(k)$ is the linear matter power spectrum, $dn/dM$ is the halo mass function and $b_h(M)$ is the halo bias.

@@

\item 1-halo covariance: note that different halo properties are not perfectly correlated due to e.g. hidden variables (age, merger history, environment etc.). I.e. in almost all cases
  \begin{equation}
    \langle U(k|M) V(k|M)\rangle\neq\langle U(k|M)\rangle\langle V(k|M)\rangle.
  \end{equation}
  In the particular case of the cross-correlation between tSZ flux and galaxy overdensity, we will model the scatter between both quantities by introducing one additional parameter $\rho_{yg}$:
  \begin{equation}
    \langle u_g(k) u_y(k)\rangle = (1+\rho_{yg})\langle u_g(k)\rangle \langle u_y(k)\rangle.
  \end{equation}
\end{itemize}
We will start by implementing these as defined in the papers, and then decide which parameters of them to free up (an obvious one is $1-b$, but we may want to be more general than that).

@@

Finally, it is easy to incorporate the fact that we may only be able to observe a fraction $f_c$ of the centrals, in which case the two profile moments read:
\begin{align}
 \langle u({\bf k})\rangle
 &=n_g^{-1}\bar{N_c}\left[f_c+\bar{N}_s\,u_{\rm NFW}(k|M)\right]\\
  \langle |u({\bf k})|^2\rangle
  &=n_g^{-2}\bar{N}_c\left[2f_c\bar{N}_s\,u_{\rm NFW}({\bf k})+\bar{N}_s^2u_{\rm NFW}^2({\bf k})\right]
\end{align}
